---
title: "ITEC 620 - Assignment 2"
author: "Johnson ODEJIDE"
date: "2022-11-06"
output: word_document
---

## Load required libraries
```{r}
library(tidyverse) # Required for forecasting - HoltsWinter
library(arules) # Required for association rules - apriori
```

# ***Section 1 - Association Rules***
## Read data from csv file
```{r}
principal <- read_csv("../../assignments/02/Dataset/Principal.csv", show_col_types = FALSE)
```

## Transform data to binary from numbers
```{r}
principal.binary <- principal >= 0.1
```

# (A)
```{r}
rules <- apriori(principal.binary, parameter = list(supp = 0.03, conf = 0.08))
princip.rules <- sort(rules, by = "confidence")
inspect(princip.rules)
```

# (B)
With a lift ratio of 0.61, it simply means that it is 61% less likely that those with Bond Index also have a stock index. We could say that the relationship is negligible.


# ***Section 2 - Forecasting***
## Read csv from file
```{r}
phoneplans <- read_csv("../../assignments/02/Dataset/PhonePlans.csv", show_col_types = FALSE)
```

# (A)

## Plot of the time series for Land lines in Developing Countries
```{r}
landlinedeving.ts <- ts(phoneplans$LandLinesDeveloping, start = 2005, frequency = 1)
plot(landlinedeving.ts)
```

# (B)

## Single Exponential Model for Land lines for Developing Countries
```{r}
model_landdeving.SESmodel <- HoltWinters(landlinedeving.ts, beta = FALSE, gamma = FALSE)
plot(model_landdeving.SESmodel, main = "Land lines for developing countries")
```

## Single Exponential model for Mobile plans for developing countries
```{r}
mobplandeving.ts <- ts(phoneplans$MobilePlansDeveloping, start = 2005, frequency = 1)
model_mobplandeving.SESmodel <- HoltWinters(mobplandeving.ts, beta = FALSE, gamma = FALSE)
plot(model_mobplandeving.SESmodel, main = "Mobile plans for developing countries")
```


# (C)
## Predict number of land lines for developing countries in 2022
The number of land lines for developing countries in 2022 is predicted to be ***471***
```{r}
predict(model_landdeving.SESmodel, 1)
```

## Predict the number of mobile plans for developing countries in 2022
The number of mobile plans for developing countries in 2022 is predicted to be ***6921***
```{r}
predict(model_mobplandeving.SESmodel, 1)
```

# (D)
Yes, a double exponential smoothing model would be more appropriate in this case because there is a ***trend*** which is upward in the case of mobile plan and downward in the case of land lines.