---
title: "Assignment 1"
author: "Johnson ODEJIDE"
date: "2022-10-31"
output: word_document
---

```{r}
library(tidyverse)
library(cluster)
library(DMwR)

Damon <- read_csv("../Dataset/Damon.csv", show_col_types = FALSE)
```

# 1. R and Descriptive Statistics

## a.) 12th Movie in the dataset
*Answer*: ***Ocean's Thirteen***
```{r}
Damon[12 , ]
```

## b.) Average value of box office
*Answer*: ***175.3548***
```{r}
mean(Damon$BoxOffice)
```

## c.) Lowest rating in the dataset
*Answer*: ***5.6***
```{r}
min(Damon$Rating)
```

## d.) Rows of the dataset containing movies with a rating of 8 or higher.
```{r}
Damon[(Damon["Rating"] >= 8), ]
```

## c.) Resulting 3 centroids
*Centroids* - **5.9**, **6.9**, and **7.7**
```{r}
Damon %>% 
  select(Rating, BoxOffice) %>% 
  scale() -> Damon.norm

set.seed(12345)

Damon.kmcluster <- kmeans(Damon.norm, 3, nstart = 10)

unscale(Damon.kmcluster$centers, Damon.norm)
```

## c.) What the centroids tell us

By looking at the centroids for cluster 1, we can conclude that on average, all the observations have 5.9 ratings and made $104.4M at the box office worldwide. Similarly, for cluster 2, the average ratings for the observations within this cluster are 6.9 and they made $93.7M at the box office worldwide, and for cluster 3, there is an average of 7.7 ratings and $366.7M at the box office worldwide among the observations.

## c.) Number of movies in each of the three clusters
**Cluster 1** has ***7 movies***
**Cluster 2** has ***15 movies***
**Cluster 3** has ***9 movies***

```{r}
Damon.kmcluster$size
```