---
title: "Multiple Regression Model"
author: "Johnson ODEJIDE"
date: "2022-11-15"
output: html_document
---

The folder structure to locate the dataset is given below: 

***BizAnalytics > assignments > 08 > Dataset***

The dataset named ***BloodPressure.csv*** contains four variables - Age, Weight, Female and BloodPressure.

The goal is to fit a linear regression model to predict the blood pressure given the age, weight, and gender of a person.

The regression equation is given below:

***E(y) = b0 + b1x1 + b1x2 + b1x3***

where *y* is the independent (Response) variable - ***Blood Pressure***

*b0* is the *intercept* 

*b1* is the *co-efficient* of the independent (Predictor) variable x1 - *Age*

*b2* is the *co-efficient* of the independent (Predictor) variable x2 - *Weight*

*b3* is the *co-efficient* of the independent (Predictor) variable x3 - *Female*



### Load library
```{r}
# To install tidyverse un-comment the next line by removing the "#" character.

# install.packages("tidyverse")
library(tidyverse)
```



### Read csv file
```{r}
bp <- read_csv("../docs/dataset/08/BloodPressure.csv", show_col_types = F)

head(bp)
```


### Draw a plot to visualize the relationships
```{r}
plot(bp)
```

From the plot, we can see there is a positive relationship between BloodPressure and Weight as well as Age.

The Female is a categorical variable that indicates 1 for Female and 0 for Male, hence, it looks somewhat straight.

We may fit the model.


### Fit the model
```{r}
bp.MLModel <- lm(BloodPressure ~ Age + Weight + Female, bp)
```



### Derive the Summary
```{r}
summary(bp.MLModel)
```



### Create new data points for prediction
```{r}
new.points <- data.frame(
  Age = 40,
  Weight = 170,
  Female = 0
)
```

### Predict the new data points
```{r}
predict(bp.MLModel, newdata = new.points)
```

### Get the confidence interval at 95%
```{r}
predict(bp.MLModel, newdata = new.points, interval="prediction")
```

